The language of generalization: Probability, vagueness, and interaction

### 2018-02-12 paper/comgen-paper.Rmd
clean intro; tweak model and discussion

<!-- Learning that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to thrive in our open-ended world. -->
Extracting generalizable knowledge that extends beyond the present context is crucial to thrive in our open-ended, dynamic world. 
Yet such knowledge can be difficult to acquire: The relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding that lightning strikes tall objects).
Fortunately, we are not bound to acquiring generalizations on our own; language allow us to communicate generalizations between each other.
By sharing generalizable knowledge, we flourish collectively without individually needing to taste potentially-poisonous plants or personally witness many lightning strikes.
Furthermore, flexibly communicating generalizations from one generation to the next may be a mechanism by which culture can cumulatively evolve [@Tomasello1999; @Henrich2015].

@@

Certain linguistic expressions encode generalizations.
The *language of generalization* is most commonly studied with *generic language* (or, *generics*), generalizations about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
<!-- Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008].  -->
In contrast to statements about concrete individuals or events (e.g., "Rufus is friendly"), generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dog}) and convey information that extends beyond the here and now, a fact which children as young as 2 appreciate [@Cimpian2008].
<!-- Additionally, generics are the primary way by which speakers discuss social categories, and thus are key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010]. -->
Generics are just one case in the language of generalization, however; events can be described in generalization (*habitual language*; e.g., "Mary swims after work.") as well as causal relationships (*causal language*; e.g., "Staring at the sun makes you go blind.").
It is believed every language can express generalization [@Behrens2005; @Carlson1995] and that such language is central to the growth of conceptual knowledge [@Gelman2004].
<!-- Thus, an understanding of the language of generalization that extends to a wide variety of types (e.g., categories, events, causes)  -->

@@

Despite its ubiquity and relative morphosyntactic simplicity, there have been few formal models of the language of generalization and none that have made precise, quantitative predictions to match human intuitions. 
The major challenge in formalizing generalization in language is determining *what makes the statements true or false*.
When we hear "Dogs bark", it sounds like a universal statement, as in "All dogs bark".
But the property does not apply to all dogs: Basenji dogs are barkless,
<!-- ^[ -->
<!-- http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html -->
<!-- ],  -->
for example.
The generalization could signal something weaker like "Most dogs bark".
However, most mosquitos do not carry malaria (in fact, only a tiny fraction do), but "Mosquitos carry malaria" is intuitively true.
<!-- *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true. -->
The only *quantifier* that would permit such a statement would be "some" (e.g., "Some mosquitos carry malaria").
But weakening the generalization to mean "some" is too permissive: Some robins are female (in fact, half of them are), but asserting "Robins are female" seems odd.
Even more perplexing: Those very same female robins lay eggs, and "Robins lay eggs" is a perfectly fine thing to say.

These observations have led to the conclusion that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not the only factor that goes into making a generalization true or false.
The predominantly studied generic statements are thought to refer to *kinds* [@Leslie2008] and thus may the linguistic manifestation of special, kind--property relations [@Prasada2000; @Prasada2012]. 
<!-- Conceptual accounts of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].  -->
"Bishops move diagonally" not because bishops tend to move diagonally but rather because those are the rules of the game.
The study of what makes generalizations true or false then reduces to a study of concepts [@carlson2009concepts] and kind--property relations [@Prasada2013].
<!-- It's been suggested that the mind has cognitive primitives that directly dictate what generalizations are true or false. -->
<!-- One such primitive is the ability to priviledge *characteristic features*: For an animal, their mode of reproduction is a characteristic feature.  -->
<!-- Thus, whatever their mode of reproduction may be will make a true generic statement (e.g., "Robins lay eggs"), regardless of the actual prevalence of the feature. -->
<!-- *Horrifying* or *striking* information is also priviledged and creates true generics, which is why "Mosquitos carry malaria" is true -->

Yet, purely arbitrary relationships can result in true generalizations [@Nickel2008; @Nickel2016; @Sterken2015].
Ravens and toasters have no priviledged relationship to each other, but "Ravens are bigger than toasters" is still true.
An understanding of generalizations just in terms of conceptual relations must be supplemented with the proviso that, in some situations, the actual prevalence of the feature matters for making generalizations true.

@@

What we are left with is hybrid theories, which try to classify different kinds of generalizations and the various inferences they support [@Prasada2013].
But insofar as there is a single class of linguistic expressions that convey generalization, there should be something common to them all: a general, unified semantic core.
In this paper, we propose such a semantic core for the language of generalization.
To do so, we look to probability, the universal currency of belief and a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication in the language of generalization. 
To formalize a model of endorsement (i.e., what makes the statements true or false), we consider the information-theoretic function of a generalization by explicitly modeling the background knowledge a language interpreter would bring to bear when understanding generalizations.
We create an endorsement model based on this interpretation hypothesis, providing the first formal theory that makes quantitative predictions about what makes generalizations in language true or false.
The assumptions of the theory, and in turn, the conditions under which the theory may be meaningfully tested are made explicit by its instantiation in a formal model.
Though conceptual structure of kind discussed of the sort discussed by Leslie and Prasada are not explicitly formalized in our model, our general cognitive modeling framework provides natural avenues for future integration.

@@

The paper is organized as follows. 
In Section 1, we formalize the hypothesis that the core of meaning of a generalization in language is simple but *underspecified*, articulate a thory of relevant background knowledge used to understand a generalization in language, and develop a computational model of endorsement around these components.
The endorsement model's predictions depend upon the background knowledge and the prevalence communicated, which we demonstrate via simulation.
Sections 2 - 4 present our three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
Across these three case studies, we both measure and manipulate background knowledge and the prevalence communicated, measuring their effects on endorsement. 
We find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements, where alterantive models fall short.
This work opens the door to understanding generalizations in richer, pragmatic language understanding contexts and building models that learn abstract knowledge from language.

@@

<!-- How do we come to know things?  -->
How does one acquire inductive beliefs?
If you *observe* wugs that have two legs, you might infer that all wugs have two legs.
But not all properties have such strong projectibility (prevalence).
Seeing a wug with broken wings tells you comparatively less about other wugs having broken wings [@Nisbett1983].
Abstract, potentially domain-specific, beliefs about properties can be represented by a probability distribution over the prevalence $P(p_{fk})$ [@Kemp2008].^[
  We adopt the following notational conventions: $p_{fk} = p(f \mid k)$ as prevalence of feature $f$ for a category $k$. 
]
Learning, then, can proceed via Bayes' Rule: $P(p_{fk} \mid d) \propto P(d \mid p_{fk}) \cdot P(p_{fk})$ given one's observational data $d$ and the observer's beliefs about the generative process that resulted in the observed data (the likelihood: $P(d \mid p_{fk})$).

But we do not always have access to observational data $d$.
Instead, we must listen to others to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically unlikely (e.g., *lightning strikes tall objects*).
Fortunately, language provides simple ways of communicating generalizations.

@@

The language of generalization is easy to spot when a property is predicated of a category: "Ks F" (e.g., "Dogs bark").
This is often called *generic language* or *generics* [@Carlson1977].
But generalization can also manifest when describing an individual (*habitual language*; e.g., "John smokes").
Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an intance of a causal event (*causal language*; e.g., "Staring at the sun makes you go blind"). ^[
  We adopt this somewhat idiosyncratic categorization in order to emphasize the different semantic types predicated. 
  Some authors refer to all of these types as *generics*.
  Still, however, the primary "generics" investigated in the literature have been generalizations about categories ("Ks F").
]
Psychologists, linguists, and philosphers have long studied the language of generalization, as it appears very simple (e.g., syntactically) yet its meaning is difficult to formalize.^[
  We take up the problem of formalizing a *meaning* for the language of generalization as opposed to the problem of *identifying* generalizations. 
  Syntax alone is neither necessary nor sufficient for a listener to know that the sentence conveys a generalization  (e.g., indefinite singulars can encode generalizations: "A dog has four legs" and bare plurals may not: "Dogs are on my front lawn").
  Our analysis thus begins once a sentence has been disambiguated as conveying a generalization. 
]

If generalization from observations can be described by a probability $p_{fk}$, it is natural to posit that same construct will be at the heart of a semantic theory of the language of generalization.
The semantic tools of *truth values* provide a way to update a state of knowledge by relating the semantic quantity (probability) to  Boolean values [@Montague1973].
The simplest way to relate a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
Thus, the simplest semantics for a generalization about category K with property F is a threshold on the *prevalence*: $\denote{K \text{ } F}(p_{fk}, \theta) = \{p_{fk} >\theta\}$.

@@

The simplest semantics for a generalization is a threshold function: $\denote{gen}(p_{fk}, \theta) = \{p_{fk} >\theta\}$, but what threshold is appropriate?
Quantifier statements can be described using particular values of $\theta$: $\denote{some}(p_{fk}) = \{p_{fk} > 0\}; \denote{all} = \{p_{fk} = 1\}$.
The extreme flexiblity of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no fixed threshold would suffice. 
Indeed, no particular threshold can suffice: The semantics of the language of generalizations is *underspecified*.
To resolve this underspecification, we hypothesize that $\theta$ is determined by context, in a way analagous to how gradable adjectives like "tall" have contextually-determined thresholds [e.g., what counts as "tall" for a four-year-old is different than what counts as "tall" for an adult; @Kennedy2007; @Lassiter2013].

@@

We can formalize this underspecified semantics in a Bayesian cognitive model, where the threshold $\theta$ is sampled from a uniform prior distribution over possible thresholds $P(\theta)$ [@Lassiter2013; @Lassiter2015; cf., @Qing2014].
The model also has prior knowledge about the property $P(p_f)$ and so literal interpretation is given by updating these prior beliefs according the truth-functional meaning of utterance $u$:

@@

Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(p_{fk}, \theta)}$ that returns probabilities proportional to $1$ when the utterance is true (i.e., when $p_{fk} > \theta$) and $0$ otherwise.
Following @Lassiter2015, we defined $P(\theta)$ to be a uniform distribution over the support of $P(p_{fk})$.

@@

@@

Given the above model of literal interpretation, how do we decide when a statement conveying a generalization is true or not?
We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization convey the appropriate information to the naive interpreter? 
We formalize this by considering how well the generalization would convey the prevalence $p_{fk}$ to the $Lit$ model (Eq. \ref{eq:L0})^[
  A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $p_{fk}$ that it wants to communicate.
  Rather, the endorser may have a distribution over $p_{f}$ for the category $k$, corresponding to the endorser's uncertain beliefs about the prevalence. 
  In this situation, we would define the endorsement model decision to be with respect to the expected value of the informativity, which integrates over the endorsement model's belief distribution:
  $S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{p_{fk}\sim P_{k}} \ln{ \int_{\theta} Lit(p_{fk}, \theta \mid u)} \diff \theta )}$
  For the empirical case studies described below, these two versions of the model make almost identical predictions.
].

@@

The uncertain, truth-conditional threshold $\theta$ is resolved by the literal interpretation model $Lit$ (Eq. \ref{eq:L0}) by integrating the model's prior beliefs about the feature in question---the *prevalence prior* $P(p_fk)$---with the underspecified semantics.
Because $P(\theta)$ is assumed to be a uniform distribution across all contexts, a generalization could in principle be felicitious with any referent-prevalence. 
However, the interpretation model's *a priori* beliefs $P(p_fk)$ must be considered before the endorsement model can say whether or not would it want to update those beliefs by endorsing the statement.

@@

Beliefs about properties result from internal conceptual models of the world. 
Without appealing to domain specific knowledge, one can construct a prior distributions over prevalence by considering the prevalence of the feature among *different* categories.
For example, many different kinds of animals *do not bark* (more precisely: have close to 0 exemplars who bark); thus, the prevalence prior for the feature *barks* $P(p_{barks})$ should have substantial probability mass near 0, because one would a randomly-sampled category to have 0 or close to 0 exemplars that bark.
Furthermore, among the categories that do have exemplars which bark (e.g., *dogs*, *seals*, ...), the probability is quite high that an exemplar will bark; thus, the corresponding prevalence prior would have substantial mass at relatively high prevalences, potentially with some uncertainty; Figure\ \@ref(fig:simulations); row 1, column 1).
Abstract beliefs between different kinds of categories would manifest in these prevalence priors in the form of multi-modal distributions; for example, the prevalence prior for *lays eggs* should similiarly have substantial probability mass near 0 (since many animal categories do not have egg-layers) but should have a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property (Figure\ \@ref(fig:simulations)A; row 1, column 4).

By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability that an entity with a certain property $f$ is a member of kind $k$: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a mosquito, upon learning that it carries malaria). 
This statistic has been shown to be highly correlated with endorsements of generalizations about categories, or *generics* [@Khemlani2012].
*Cue validity* implicitly encodes knowledge of other categories, by averaging over those categories $k'$ via the normalizing constant in Bayes' Rule:
$P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}$.
Since cue validity is defined for a particular category--property pair, it can be seen as a point estimate of the prevalence prior distribution.
In particular: The normalizing constant for calculating cue validity ($\sum_{k' \in K} p_{fk'} \cdot P(p_{fk'} )$) is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p_{f})]$.
For a slower derivation of this relationship, see Appendix A.

@@

The literal interpretation model computes a posterior distribution on prevalence by considering different possible thresholds $\theta$.
Figure\ \@ref(fig:uniformPriorSimulation) shows different components of the model behavior assuming a uniform prevalence prior. 
If the threshold were to be very high (e.g., $\theta = 0.75$), only the highest prevalence levels would be consistent with the utterance (Figure\ \@ref(fig:uniformPriorSimulation)A, right).
As the threshold decreases, more and more prevalence levels would be true  (Figure\ \@ref(fig:simulations)A).
The uncertain-threshold interpretation model averages over these possibilities, resulting in a posterior distribution that favors higher prevalence levels (Figure\ \@ref(fig:uniformPriorSimulation)B).
The endorsement model thus predicts higher rates of endorsement as the speaker's belief about the prevalence (referent-prevealence) increases (Figure\ \@ref(fig:uniformPriorSimulation)C).

@@

The uncertain-threshold model's interpretations are highly sensitive to the shape of the prevalence priors (Figure\ \@ref(fig:simulations)).
Hearing "Ks bark" tells the literal interpretor that *almost all* Ks bark, though there is a good deal of uncertainty in the precise quantity (column 1).
"Ks lay eggs" has a strikingly different interpretation: It means "Half of Ks lay eggs" (column 4).
The interpretation model can also derive very weak interpretation, as shown in the  *carries malaria* distribution (column 6).

The endorsement model (Eq. \ref{eq:S1}) predicts endorsement probabilities based on the literal interpretation of the utterance and the referent-category prevalence (e.g., how many robins lay eggs; shown in arrows in Figure\ \@ref(fig:simulations)A).
Predictions for a few examples are shown in the bottom row of Figure\ \@ref(fig:simulations).
In accord with intuition, the endorsement model predicts "Dogs bark", "Robins lay eggs", and "Mosquitos carry malaria" are all true, despite the referent-prevalences varying substantially between these three examples. 
Intruigingly, the model predicts "Robins are female" (which has the same prevalence as "Robins lay eggs") should receive intermediate endorsement: It is neither true nor false.
To understand this prediction, examine the interpretation distribution for the *are female* property: It is identical with the prior (Figure\ \@ref(fig:simulations); column 5; top vs. bottom row).
The endorsement model decides that is neither better nor worse to produce the generalization than to stay silent, as they both carry the same information content.
This example can be contrasted with cases such as "Sharks don't eat people" and "Kangaroos have spots", which the model thinks would be misleading to say (i.e., better to say nothing).

>>>>

<!-- Learning that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to thrive in our open-ended world. -->
Acquiring understanding that extends beyond the present context is crucial to thrive in our open-ended, dynamic world. 
Yet such knowledge can be difficult to extract from the environment: The relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding that lightning strikes tall objects).
Fortunately, we are not bound to acquiring generalizations on our own; language allow us to communicate generalizations between each other.
By sharing generalizable knowledge, we flourish collectively without individually needing to taste potentially-poisonous plants or personally witness many lightning strikes.
Furthermore, flexibly communicating generalizations from one generation to the next may be a mechanism by which culture can cumulatively evolve [@Tomasello1999; @Henrich2015].

@@

<!-- Certain linguistic expressions encode generalizations. -->
<!-- Language provides multiple, distinct ways of encoding generalizations. -->
The *language of generalization* is most commonly studied with *generic language* (*generics*) or generalizations about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
<!-- Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008].  -->
In contrast to statements about concrete individuals or events (e.g., "Rufus is friendly"), generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dog}) and convey information that extends beyond the here and now, a fact which children as young as 2 appreciate [@Cimpian2008].
<!-- Additionally, generics are the primary way by which speakers discuss social categories, and thus are key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010]. -->
Generics are just one case in the language of generalization, however; events can be described in generalization (*habitual language*; e.g., "Mary swims after work.") as well as causal relationships (*causal language*; e.g., "Staring at the sun makes you go blind.").
It is believed every language can express generalization [@Behrens2005; @Carlson1995] and that such language is central to the growth of conceptual knowledge [@Gelman2004].
<!-- Thus, an understanding of the language of generalization that extends to a wide variety of types (e.g., categories, events, causes)  -->

@@

Despite its ubiquity and relative morphosyntactic simplicity, there have been few formal models of the language of generalization and none that have made precise, quantitative predictions that match human intuitions. 
The major challenge in formalizing generalization in language is determining what makes the statements true or false.
When we hear "Dogs bark", it sounds like a universal statement, as in "All dogs bark".
But the property does not apply to all dogs: Basenji dogs are barkless,
<!-- ^[ -->
<!-- http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html -->
<!-- ],  -->
for example.
The generalization could signal something weaker like "Most dogs bark".
However, *most* mosquitos do not carry malaria (in fact, only a tiny fraction do), but "Mosquitos carry malaria" is intuitively true.
<!-- *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true. -->
The only *quantifier* that would permit such a statement would be *some* (e.g., "Some mosquitos carry malaria").
But weakening the generalization to mean *some* is too permissive: Some robins are female (in fact, half of them are), but endorsing "Robins are female" seems odd.
Even more perplexing: Those very same female robins lay eggs, and "Robins lay eggs" is a perfectly fine thing to say.

These observations have led some to conclude that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not the only factor that goes into making a generalization true or false.
The predominantly studied generic statements are thought to refer to *kinds* [@Leslie2008] and thus may the linguistic manifestation of special, kind--property relations [@Prasada2000; @Prasada2012]. 
<!-- Conceptual accounts of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].  -->
"Bishops move diagonally" not because bishops tend to move diagonally but rather because those are the rules of the game.
The study of what makes generalizations true or false then reduces to a study of concepts [@carlson2009concepts] and kind--property relations [@Prasada2013].
<!-- It's been suggested that the mind has cognitive primitives that directly dictate what generalizations are true or false. -->
<!-- One such primitive is the ability to priviledge *characteristic features*: For an animal, their mode of reproduction is a characteristic feature.  -->
<!-- Thus, whatever their mode of reproduction may be will make a true generic statement (e.g., "Robins lay eggs"), regardless of the actual prevalence of the feature. -->
<!-- *Horrifying* or *striking* information is also priviledged and creates true generics, which is why "Mosquitos carry malaria" is true -->

Yet, purely arbitrary relationships can also result in true generalizations [@Nickel2008; @Nickel2016; @Sterken2015].
Ravens and toasters have no privileged relationship to each other, but "Ravens are bigger than toasters" is still true.
An understanding of generalizations just in terms of conceptual relations must be supplemented with the proviso that, in some situations, the actual statistics of the feature matters for making generalizations true.

@@

What we are left with is hybrid theories, which try to classify different kinds of generalizations and the various inferences they support [@Prasada2013].
But insofar as there is a single class of linguistic expressions that convey generalization, there should be something common to them all: a general, unified semantic core.
In this paper, we propose such a semantic core for the language of generalization.
To do so, we look to probability, the universal currency of belief and a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication in the language of generalization. 
To formalize a model of endorsement (i.e., what makes the statements true or false), we consider the communicative function of a generalization by explicitly modeling the background knowledge a language interpreter would bring to bear when understanding generalizations.
We create an endorsement model based on this interpretation hypothesis, providing the first formal theory that makes quantitative predictions about what makes generalizations in language true or false.
The assumptions of the theory, and in turn, the conditions under which the theory may be meaningfully tested are made explicit by its instantiation in a formal model.
Though conceptual structure of kind discussed of the sort discussed by Leslie and Prasada are not explicitly formalized in our model, our general cognitive modeling framework provides natural avenues for future integration.

@@

The paper is organized as follows. 
In Section 1, we formalize the hypothesis that the core of meaning of a generalization in language is simple but *underspecified*, articulate a theory of relevant background knowledge used to understand a generalization in language, and develop a computational model of endorsement around these components.
The endorsement model's predictions depend upon the background knowledge and the prevalence communicated, which we demonstrate via simulation.
Sections 2-4 present our three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
Across these three case studies, we both measure and manipulate background knowledge and the prevalence communicated, measuring their effects on endorsement. 
We find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements, where alternative models fall short.
This work opens the door to understanding generalizations in richer, pragmatic language understanding contexts and building models that learn abstract knowledge from language.

@@

<!-- How do we come to know things?  -->
How does one acquire inductive beliefs?
If you *observe* wugs that have two legs, you might infer that all wugs have two legs.
But not all properties have such strong projectibility (prevalence).
Seeing a wug with broken wings tells you comparatively less about other wugs having broken wings [@Nisbett1983].
Abstract, potentially domain-specific, beliefs about properties can be represented by a probability distribution over the prevalence $P(p_{fk})$ [@Kemp2008].^[
  We adopt the following notational simplification: $p_{fk} = p(f \mid k)$. 
]
Learning, then, can proceed via Bayes' Rule: $P(p_{fk} \mid d) \propto P(d \mid p_{fk}) \cdot P(p_{fk})$ given one's observational data $d$ and the observer's beliefs about the generative process that resulted in the observed data---the likelihood $P(d \mid p_{fk})$.

<!-- But we do not always have access to  -->
Observational data $d$ is not always available, however.
Instead, we must listen to others to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*), events that are statistically unlikely (e.g., *lightning strikes tall objects*), or just aspects of the world that we have yet to experience.
Fortunately, language provides simple ways of communicating generalizations.

@@

The language of generalization is easy to spot when a property is predicated of a category: "Ks F" (e.g., "Dogs bark").
This is often called *generic language* or *generics* [@Carlson1977].
But generalization can also manifest when describing an individual (*habitual language*; e.g., "John smokes").
Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an instance of a causal event (*causal language*; e.g., "Staring at the sun makes you go blind"). ^[
  We adopt this somewhat idiosyncratic categorization in order to emphasize the different semantic types predicated. 
  Some authors refer to all of these types as *generics*.
  Still, however, the primary "generics" investigated in the literature have been generalizations about categories ("Ks F").
]
Psychologists, linguists, and philosophers have long studied the language of generalization, as it appears very simple (e.g., syntactically) yet its meaning is difficult to formalize.^[
  We take up the problem of formalizing a *meaning* for the language of generalization as opposed to the problem of *identifying* generalizations. 
  Syntax alone is neither necessary nor sufficient for a listener to know that the sentence conveys a generalization  (e.g., indefinite singulars can encode generalizations: "A dog has four legs" and bare plurals may not: "Dogs are on my front lawn").
  Our analysis thus begins once a sentence has been disambiguated as conveying a generalization. 
]

If generalization from observations can be described by a probability $p_{fk}$, it is natural to posit that same construct will be at the heart of a semantic theory of the language of generalization.
The semantic tools of *truth values* provide a way to update a state of knowledge by relating the semantic quantity (probability) to  Boolean values [@Montague1973].
The simplest way to relate a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
Thus, the simplest semantics for a generalization about category $k$ with property $f$ is a threshold on the *prevalence*: $\denote{K \text{ } F}(p_{fk}, \theta) = \{p_{fk} >\theta\}$.

@@

The simplest semantics for a generalization is a threshold function: $\denote{gen}(p_{fk}, \theta) = \{p_{fk} >\theta\}$, but what threshold is appropriate?
Quantifier statements can be described using particular values of $\theta$: $\denote{some}(p_{fk}) = \{p_{fk} > 0\}$; $\denote{all} = \{p_{fk} = 1\}$.
The extreme flexibility of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no fixed threshold would suffice. 
Rather than throw out the threshold-semantics, we posit this semantics is *underspecified*.
We hypothesize that $\theta$ is determined by context in a way analogous to how gradable adjectives like "tall" have contextually-determined thresholds [e.g., what counts as "tall" for a four-year-old is different than what counts as "tall" for an adult; @Kennedy2007; @Lassiter2013].

@@

We formalize this underspecified semantics in a Bayesian cognitive model, where the threshold $\theta$ is sampled from a uniform prior distribution over possible thresholds $P(\theta)$ [@Lassiter2013; @Lassiter2015; cf., @Qing2014].
The model also has prior knowledge about the property $P(p_fk)$ and literal interpretation is given by updating these prior beliefs according the truth-functional meaning of utterance $u$:

@@

Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(p_{fk}, \theta)}$ that returns probabilities proportional to $1$ when the utterance is true (i.e., when $p_{fk} > \theta$) and $0$ otherwise.

@@

Following @Lassiter2015, we defined $P(\theta)$ to be a uniform distribution over the support of $P(p_{fk})$.

@@

Given the above model of literal interpretation, how do we decide when a statement conveying a generalization is true or not?
We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization convey the appropriate information to the naive interpreter? 
We formalize this by considering how well the generalization would convey the prevalence $p_{fk}$ to the $Lit$ model (Eq. \ref{eq:L0}).^[
  A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $p_{fk}$ that it wants to communicate.
  Rather, the endorser may have a distribution over $p_{f}$ for the category $k$, corresponding to the endorser's uncertain beliefs about the prevalence. 
  In this situation, we would define the endorsement model decision to be with respect to the expected value of the informativity, which integrates over the endorsement model's belief distribution:
  $S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{p_{fk}\sim P_{k}} \ln{ \int_{\theta} Lit(p_{fk}, \theta \mid u)} \diff \theta )}$
  For the empirical case studies described below, these two versions of the model make almost identical predictions.
]

@@

The uncertain, truth-conditional threshold $\theta$ is resolved by the literal interpretation model $Lit$ (Eq. \ref{eq:L0}) by integrating the model's prior beliefs about the feature in question---the *prevalence prior* $P(p_{fk})$---with the underspecified semantics.
Because $P(\theta)$ is assumed to be a uniform distribution across all contexts, a generalization could in principle be felicitous with any referent-prevalence. 
However, the interpretation model's prior beliefs $P(p_{fk})$ must be considered before the endorsement model can say whether or not would it want to update those beliefs by endorsing the statement.

@@

Beliefs about properties result from internal conceptual models of the world. 
Without appealing to domain specific knowledge, one can construct a prior distributions over prevalence by considering the prevalence of the feature among *different* categories.
For example, many different kinds of animals *do not bark* (more precisely: have close to 0 exemplars who bark); thus, the prevalence prior for the feature *barks* $P(p_{barks})$ should have substantial probability mass near 0, because one would expect a randomly-sampled category to have 0 or close to 0 exemplars that bark.
Furthermore, among the categories that do have exemplars which bark (e.g., *dogs*, *seals*, ...), the probability is quite high that an exemplar will bark; thus, the corresponding prevalence prior would have some probability mass at relatively high prevalences, potentially with some uncertainty (Figure\ \@ref(fig:simulations); column 1).
Abstract beliefs between different kinds of categories could manifest in these prevalence priors in the form of multi-modal distributions; for example, the prevalence prior for *lays eggs* should similarly have substantial probability mass near 0 (since many animal categories do not have egg-layers) but should have a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property (Figure\ \@ref(fig:simulations); column 4).

By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability that an entity with a certain property $f$ is a member of kind $k$: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a mosquito, upon learning that it carries malaria), shown to be highly correlated with endorsements of generics [@Khemlani2012].
*Cue validity* implicitly encodes knowledge of other categories $k'$ by averaging over those categories via the denominator in Bayes' Rule:
$P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}$.
Since cue validity is defined for a particular category--property pair, it can be seen as a point estimate of the prevalence prior distribution.
In particular: The normalizing constant for calculating cue validity ($\sum_{k' \in K} p_{fk'} \cdot P(p_{fk'} )$) is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p_{fk})]$.
For a more detailed derivation of this relationship, see Appendix A.

@@

The literal interpretation model computes a posterior distribution on prevalence by considering different possible thresholds $\theta$.
Figure\ \@ref(fig:uniformPriorSimulation) shows different components of the model behavior assuming a uniform prevalence prior. 
If the threshold were to be very high (e.g., $\theta = 0.75$), only the highest prevalence levels would be consistent with the utterance (Figure\ \@ref(fig:uniformPriorSimulation)A, right).
As the threshold decreases, more and more prevalence levels would be true  (Figure\ \@ref(fig:simulations)A).
Roughly speaking, the uncertain-threshold interpretation model averages over these possibilities, resulting in a posterior distribution that favors higher prevalence levels because they are consistent with more thresholds (Figure\ \@ref(fig:uniformPriorSimulation)B).
The endorsement model inverts the interpretation model and predicts higher rates of endorsement as the speaker's belief about the prevalence (referent-prevalence) increases (Figure\ \@ref(fig:uniformPriorSimulation)C).

@@

The uncertain-threshold model's interpretations are highly sensitive to the shape of the prevalence priors (Figure\ \@ref(fig:simulations)).
Hearing "Ks bark" tells the literal interpreter that *almost all* Ks bark, though there is a good deal of uncertainty in the precise quantity (column 1).
"Ks lay eggs" has a strikingly different interpretation: It means "Half of Ks lay eggs" (column 4).
The interpretation model can also derive very weak interpretation, as shown in the  *carries malaria* distribution (column 6).

The endorsement model (Eq. \ref{eq:S1}) predicts endorsement probabilities based on the literal interpretation of the utterance and the referent-category prevalence (e.g., how many robins lay eggs; shown in arrows in Figure\ \@ref(fig:simulations)A).
Predictions for a few examples are shown in the bottom row of Figure\ \@ref(fig:simulations).
In accord with intuition, the endorsement model predicts "Dogs bark", "Robins lay eggs", and "Mosquitos carry malaria" are all true, despite the referent-prevalences varying substantially between these three examples. 
Intriguingly, the model predicts "Robins are female" (which has the same prevalence as "Robins lay eggs") should receive intermediate endorsement: It is neither true nor false.
To understand this prediction, examine the interpretation distribution for the *are female* property: It is identical with the prior (Figure\ \@ref(fig:simulations); column 5; top vs. bottom row).
The endorsement model decides that is neither better nor worse to produce the generalization than to stay silent, as they both carry the same information content.
This example can be contrasted with cases such as "Sharks don't eat people" and "Kangaroos have spots", which the model thinks would be misleading to say (i.e., better to say nothing).

These simulations show how the model predicted endorsement depends upon the background knowledge about the property $P(p_f)$ as well as the referent-prevalence $p_{fk}$ communicated. 
We chose schematic values for each of these, and saw that the endorsement model recovers standard intuitions about the truth or falsity of classic examples from the generics literature.
In what follows, we test this theory for a wide range of generalizations, including generalizations of different types (categories, events, and causes).
We do this by both measuring and manipulating background knowledge and referent-prevalence and relate it to human elicited endorsements of generalizations.
